\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{a4paper, margin=1in}

\title{Ethan O'Conner}
\author{Clarity Studios}
\date{\today}

\begin{document}

\maketitle

\begin{center}
    \textbf{Contact Information:}
    \ \href{tel:+16309030420}{630-903-0420} \
    \href{mailto:claritystudio@proton.me}{claritystudio@proton.me} \
    Location: Chicago, IL, USA
\end{center}

\section{Profile}
A seasoned wedding photographer with a passion for capturing timeless moments, Ethan O'Conner founded \textbf{Clarity Studios} at the age of 18. With a keen eye for detail, he specializes in wedding photography that emphasizes natural beauty, candid moments, and intimate atmospheres. Known for blending classical techniques with modern aesthetics, Ethan's work has garnered recognition in both local and national wedding photography circles.

\section{Personal Information}
\begin{itemize}
    \item \textbf{Full Name:} Ethan O'Conner
    \item \textbf{Nationality:} American
    \item \textbf{Languages:} English (Fluent)
\end{itemize}

\section{Education}
\begin{itemize}
    \item \textbf{High School Diploma}, 2024
    \item \textbf{Photography Courses:} 
    \begin{itemize}
        \item Online Wedding Photography Masterclass, 2022
        \item Advanced Lighting Techniques, 2021
    \end{itemize}
\end{itemize}

\section{Work Experience}
\textbf{Owner/Photographer at Clarity Studios}, 2024–Present \
Clarity Studios has successfully photographed over 150 weddings across the United States. The company is known for its high-quality, customizable photography packages and exceptional attention to detail in wedding day photography.

\begin{itemize}
    \item Photographed over 150 weddings in the past two years, each with unique, personalized approaches.
    \item Managed a team of 3 assistant photographers for large-scale weddings and events.
    \item Developed an efficient post-production workflow, ensuring timely delivery of wedding albums to clients within 2-3 weeks.
    \item Built a strong portfolio with a mix of classic, romantic, and modern wedding photography styles.
    \item Regularly updated the company's portfolio and social media with fresh content.
\end{itemize}

\section{Notable Weddings Photographed}
\begin{itemize}
    \item \textbf{Sarah and Daniel Edwards} – The Ritz-Carlton, Chicago, IL (March 2024)
    \item \textbf{Olivia and James Price} – The Drake Hotel, Chicago, IL (July 2023)
    \item \textbf{Grace and David Thomas} – Navy Pier, Chicago, IL (August 2023)
    \item \textbf{Emily and Michael Reed} – The Langham, Chicago, IL (May 2023)
    \item \textbf{Anna and Samuel Carter} – Lake Geneva, WI (September 2023)
    \item \textbf{Jessica and Ryan Ford} – Oakbrook Hills Resort, Oak Brook, IL (November 2023)
    \item \textbf{Chloe and Liam Grant} – Four Seasons Hotel, Chicago, IL (June 2023)
    \item \textbf{Sophia and Alex McCarthy} – Belvedere Banquets, Elk Grove Village, IL (April 2023)
    \item \textbf{Megan and Christopher Wright} – St. Charles Country Club, St. Charles, IL (March 2023)
    \item \textbf{Rachel and Benjamin Clark} – Chicago History Museum, Chicago, IL (December 2022)
\end{itemize}

\section{Skills}
\begin{itemize}
    \item Expert in DSLR, Mirrorless, and Medium Format Camera Systems.
    \item Skilled in Lightroom, Photoshop, and other photo editing software.
    \item Excellent customer service and client relations.
    \item Strong organizational and time-management abilities.
    \item Fluent in Adobe Premiere Pro for video work.
\end{itemize}

\section*{References}
Available upon request.

\end{document}